---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dht

<!-- badges: start -->
[![R build status](https://github.com/degauss-org/dht/workflows/R-CMD-check/badge.svg)](https://github.com/degauss-org/dht/actions)
<!-- badges: end -->

dht is a collection of functions to assist in building DeGAUSS containers. This includes `use_degauss_container`, which creates the files necessary to build a DeGAUSS container, as well as several other helper functions to be used within DeGAUSS containers.

## Installation

Currently, the package is only available on GitHub. Install inside R with:

``` r
# install.packages("remotes")
remotes::install_github("degauss-org/dht")
```

## Example Usage

### DeGAUSS template functions

The `use_degauss_template()` function creates the all the files needed to build a DeGAUSS container.  This includes:

   * `Dockerfile`
   * `Makefile`
   * `README.md`
   * `entrypoint.R`
   * `.dockerignore`
   * `test/my_address_file_geocoded.csv`
   * `LICENSE.md` GPL license
   * `.github/workflows/build-deply.yaml`
   
These files can then be edited before building the container.
   
### DeGAUSS helper functions

**Welcome users to DeGAUSS**

```{r}
library(dht)
greeting(geomarker_name = "roads", version = "0.1", description = "calculates proximity and length of nearby major roadways")
```

**Call libraries without startup messages**

```{r}
qlibrary(dplyr)
```


**Read in geocoded data**

```{r}
(d <- read_lat_lon_csv('tests/testthat/my_address_file_geocoded.csv', sf = T, project_to_crs = 5072))
```

Returns a list with two elements -- the raw data and tibble nested on row (to prevent calculations with duplicate lat/lon)

**Check that required columns are present**

```{r}
check_for_column(d, 'lat', d$lat)
```

Nothing is returned if the column is present.
An error is thrown if the column is not present.

**Check for column type**

```{r}
check_for_column(d, 'lat', d$lat, 'numeric')
```

Again, nothing is returned if the column type matches the desired type.

```{r}
check_for_column(d, 'lat', d$lat, 'character')
```

A warning is displayed if the column type does not match the desired type.

**Check that dates are read in correctly/reformat dates**

```{r}
check_dates(c('1/1/21', '1/2/21', '1/3/21'))
```

If dates are in slash (1/1/21) or ISO (2021-01-01) format, they are returned in ISO format. 
If dates are in another format, an error is thrown.

**Write geomarker output file**

Unnests the tibble created with `read_lat_lon_csv()` and merges back to raw data, then writes the output csv with container name and version appended to filename.

```{r, eval = F}
write_geomarker_file(d = d, 
                     raw_data = d, 
                     filename = 'tests/my_address_file_geocoded.csv', 
                     geomarker_name = 'roads', 
                     version = '0.1')
```

