---
title: "In-Line Helper Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{In-Line Helper Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dht)
```

**Welcome users to DeGAUSS**

```{r}
greeting(geomarker_name = "roads", version = "0.1", description = "calculates proximity and length of nearby major roadways")
```

**Call libraries without startup messages**

```{r}
qlibrary(dplyr)
```

**Read in geocoded data**

```{r}
(d <- read_lat_lon_csv('../tests/testthat/my_address_file_geocoded.csv', sf = T, project_to_crs = 5072))
```

Returns a list with two elements -- the raw data and tibble nested on row (to prevent calculations with duplicate lat/lon)

**Check that required columns are present**

```{r}
check_for_column(d, 'lat', d$lat)
```

Nothing is returned if the column is present.
An error is thrown if the column is not present.

**Check for column type**

```{r}
check_for_column(d, 'lat', d$lat, 'numeric')
```

Again, nothing is returned if the column type matches the desired type.

```{r}
check_for_column(d, 'lat', d$lat, 'character')
```

A warning is displayed if the column type does not match the desired type.

**Check that dates are read in correctly/reformat dates**

```{r}
check_dates(c('1/1/21', '1/2/21', '1/3/21'))
```

If dates are in slash (1/1/21) or ISO (2021-01-01) format, they are returned in ISO format. 
If dates are in another format, an error is thrown.

**Write geomarker output file**

Unnests the tibble created with `read_lat_lon_csv()` and merges back to raw data, then writes the output csv with container name and version appended to filename.

```{r, eval = F}
write_geomarker_file(d = d, 
                     raw_data = d, 
                     filename = 'tests/my_address_file_geocoded.csv', 
                     geomarker_name = 'roads', 
                     version = '0.1')
```
